\documentclass[a4paper,11pt]{article}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{ragged2e}

\geometry{margin=1in}
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=*}
\titleformat{\section}{\bfseries\large}{}{0em}{}

\begin{document}

\begin{center}
    {\LARGE \textbf{Indumathi Madhu}} \\
    \vspace{4pt}
    \href{mailto:indumathi.madhu@gwu.edu}{indumathi.madhu@gwu.edu} \,|\,
    \href{https://github.com/indum8}{https://github.com/indum8} \,|\,
    +1 571 237 3576 \\
    \href{https://www.linkedin.com/in/indumathi-madhu/}{linkedin.com/in/indumathi-madhu} \,|\,
    Washington DC, US
\end{center}
\noindent\rule{\textwidth}{0.4pt} % This draws a horizontal line across the page

\section*{Interests}
System Engineering, Robotics, CPS


\section*{Education}

\noindent
\textbf{The George Washington University}, Washington, DC, USA \hfill Aug 2024 -- Present \\
PhD in Computer Science \\[6pt]
\noindent
\textbf{Birla Institute of Technology \& Science}, Hyderabad, India \hfill Jan 2020 -- Jul 2022 \\
M.Tech. in Software Systems (Cybersecurity); GPA: 8.02/10 \\
\textit{Courses:} Cybersecurity, Network Security, Cloud \& IoT Security, Ethical Hacking \\[6pt]
\noindent
\textbf{Bharathiar University}, Coimbatore, India \hfill May 2016 -- May 2019 \\
M.Sc. in Computer Science; GPA: 7.07/10 \\
\textit{Courses:} Computer Networks, Software Engineering \\[6pt]
\noindent
\textbf{Hindusthan College of Arts and Science}, Coimbatore, India \hfill Jul 2013 -- May 2016 \\
Bachelor of Computer Applications; GPA: 7.89/10 \\
\textit{Courses:} Mathematical Structures for Computer Science, C, C++, Java Programming


\section*{Professional Experience}
\noindent
\textbf{Birla Institute of Technology and Science}\hfill 2022 -- 2024 \\
Visiting Faculty
\begin{itemize}
    \item Conceptualized and crafted laboratory experiments centered on In-Vehicle communication protocols, encompassing CAN, CAN-FD, LIN, and Ethernet. Activities included data monitoring, simulation, signal tracking, scripting, automation, PC-based data logging, and the utilization of diverse databases and file formats.
    \item Spearheaded the establishment of CAN Fuzzing test environments, encompassing scenario creation, outcomes analysis, and meticulous documentation of defects and glitches.
    \item Introduced BITLabs, an inventive Remote Desktop Control solution enabling remote access to physical lab setups from any location.
    \item Oversaw the configuration and visualization of LIDAR technology.
    \item Developed an experiment focusing on CAN bus exploitation, involving splicing into the CAN network, data capture using PCAN, and the application of reverse engineering techniques via PCAN View.
    \item Collaborated with Intrepid Control Systems on projects related to CAN, CAN-FD, LIN, and Ethernet protocols during industry immersion.
    \item Assisting students with their dissertation and practical school projects involving CAN Firewall Protection, Message Authentication Technology, Implementation of security techniques like digital watermarking in telematics control units of connected cars, FOTA in contemporary automobiles, and secure software downloads and cybersecurity measures for automotive Electronic Control Units (ECUs).
\end{itemize}
\vspace{4pt}
\noindent
\textbf{ReynLab by Sirius Motorsports}\hfill 2020 -- 2022 \\
Instructor (Deputed in BITS Pilani)
\begin{itemize}
    \item Established an Automotive Cyber Systems laboratory from the ground up, tailored to the needs of working professionals in the Automotive and Manufacturing sectors, with a thoughtful approach to course materials.
    \item Collaborated with a team of 3 to develop setups on CAN exploitation on Instrumentation Cluster and Tapping CAN messages from steer-by-wire and head unit of a Skoda.
\end{itemize}
\vspace{4pt}
\noindent
\textbf{Scoop Technologies}\hfill 2019 -- 2020 \\
Service Desk Associate (Deputed in Wipro Technologies)
\begin{itemize}
    \item L2 Engineer - Efficiently handled support tickets through chat, ensuring compliance with service level agreements, and played a crucial role in ensuring the smooth operation of IT systems and infrastructure for end-users.
\end{itemize}
\vspace{4pt}
\noindent
\textbf{Aalan Technology}\hfill 2018 -- 2019 \\
Software Trainee
\begin{itemize}
    \item Designed, developed, and implemented software applications aimed at automating and streamlining business processes within the textile industry
\end{itemize}
\vspace{4pt}
\noindent
\textbf{Cognizant Technology Solutions}\hfill 2016 -- 2018 \\
System Engineer
\begin{itemize}
    \item L1 Engineer - Ensured the seamless availability and optimal functionality of IT systems and applications while consistently providing excellent customer service
\end{itemize}


\section*{Teaching \& Mentoring Experience}
\noindent
\textbf{Design of Autonomous Systems Lab}, The George Washington University \hfill 2024 -- 2025
\begin{itemize}
    \item Teaching Assistant (2025): Python, Algorithms, Object Detection, ROS, Linux
    \item Teaching Assistant (2024): Systems Programming (C Programming)
\end{itemize}
\vspace{0.5em}
\noindent
\textbf{Automotive Cyber Systems Lab}, Birla Institute of Technology and Science \hfill 2020 -- 2024
\begin{itemize}
    \item Faculty: CAN, CAN-FD, LIN, Ethernet
\end{itemize}
\vspace{0.5em}
\noindent
\textbf{Soft Skills and Placement Trainer}, PSGR Krishnammal College of Arts and Science \hfill 2016 -- 2022
\begin{itemize}
    \item Mentor: Trained undergraduate students on soft skills, communication, aptitude, work-life balance, and resume preparation.
\end{itemize}


\section*{Selected Projects}
\begin{itemize}
    \item \textbf {Privacy-Preserving Services for Intelligent Transportation Systems with Homomorphic Encryption} -- CO2 emission prediction through the implementation of Homomorphic Encryption.
    \item \textbf {AI-based Intrusion Detection Systems for Securing Automotive Network Protocols: A Systematic Literature Review.}
\end{itemize}


\section*{Certifications}
\begin{itemize}
    \item Cyber Security in Manufacturing, University of Buffalo (2022)
    \item Diploma in Computer basics and administration, INNIVERS (2018)
\end{itemize}


\section*{Skills Summary}
\textbf{Programming:} Python, C, SQL \\
\textbf{Frameworks:} OpenCV \\
\textbf{Tools:} VehicleSpy, Vector, PCAN view\\
\textbf{Platforms:} Linux, Windows, Arduino, Raspberry Pi, Nvidia Jetson \\
\textbf{Soft Skills:} Critical thinking, R\&D team leadership, Systematic thinking


\section*{Volunteer Experience}
\begin{itemize}
    \item Organizer, BITS AUTOwn’23, Birla Institute of Technology and Science
    \item Member, Divyang Warrior’s, Birla Institute of Technology and Science
\end{itemize}


\section*{Extra Curricular Activities}
\begin{itemize}
    \item Athletics: Achieved a 16 - second sprint in the 100-meter dash.
    \item Leisure Pursuits: Encompasses swimming, gardening, dancing, culinary arts, and creative crafting
\end{itemize}


\section*{Honors}
\begin{itemize}
    \item Academic Scholarship, Birla Institute of Technology and Science.
\end{itemize}


\section*{References}
Available upon request.

\end{document}